Papers

### 2024-04-20 quarto/index.qmd
update

* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* *If you're interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>.* [Filled, see you next year]

>>>>

* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* If you're interested in <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" target="_blank">research internship</a> with our team in 2024, just <a href="img/email.png" target="_blank">email me</a>. [Filled, see you next year]
